\begin{englishabstract}

Deployed smart contracts cannot be modified, so that underlying deficiencies
cannot be patched after deployment and causes significant loss, especially
for the application in the financial field. Formal verification for smart contracts
before deployment is therefore significant.
Verification in smart contracts as well as in the other field confronts complexities
of actual programs. 
Logic information and wills of developer absent partially from concrete code
representation of programs, and complete recovery from code is hard.
If the logic information and wills were expressed completely and precisely
to enable the acquirability in analysis, verification can be effectively simplified.

The paper presents a formal system named {\it Noesis logic} and {\it noumenal semantics} 
on which the logic focuses mainly. In Noesis logic, noumenal semantics of a value or a procedure
is an abstract mathematical object which is easy to analysis and expresses the developer's
logics and wills precisely and completely. Based on the logic a smart contract construction method
is designed, that developers deduct theorems in Noesis logic to construct program and also express
  logics and wills in noumenal semantics. A tool \Eamlh is provided in this paper to implement
the method, built on the famous HOL interactive theorem prover.
Noesis logic is implemented inside HOL logic and Noesis theorems are deducted by HOL prover,
to guarantee the correctness. Noumenal semantics are represented as arbitrary objects in HOL logic,
enabling expressiveness for almost all logics and wills about programs.
Therefore, it's acceptable to enforce developers express logics and wills in noumenal semantics
precisely and completely, so that noumenal semantics contain all related properties of the program,
and as a consequence verification of complex concrete program could be reduced to relatively easier
verification of abstract mathematical object.
Finally, \Eamlh can produce executable smart contracts on blockchain platform EOS.IO, with
verified compilation procedure.

\englishkeywords{axiomatic system, formal verification, 
  type system, smart contract, program semantics}
	
\end{englishabstract}
